---
title: "Make changes to the workflow"
output: html_notebook
---

# About

When we modify the code and data of an existing workflow, `targets` automatically detects the changes, and `tar_make()` only reruns the affected targets. This notebook showcases this behavior and shows how it can save you time.

# Instructions

Throughout this chapter, you will test your understanding with quiz questions. Supply your choices to the `answer_*()` functions when you come to them. Run the code chunk below to set up the quizzes, but try not to peak in advance. It is okay to answer incorrectly at first.

```{r}
source("3-changes/utils.R")
source("3-changes/answers.R")
```

Let's clear out the old `_targets/` data store if it exists.

```{r}
library(targets)
tar_destroy() # Start fresh.
```

# Setup

Let's begin with a fresh pipeline.

```{r}
tar_script({
  source("3-changes/functions.R")
  tar_option_set(packages = c("keras", "recipes", "rsample", "tidyverse", "yardstick"))
  tar_pipeline(
    tar_target(churn_file, "data/churn.csv", format = "file"), 
    tar_target(churn_data, split_data(churn_file)),
    tar_target(churn_recipe,  prepare_recipe(churn_data)),
    tar_target(run_relu, test_model(act1 = "relu", churn_data, churn_recipe)),
    tar_target(run_sigmoid, test_model(act1 = "sigmoid", churn_data, churn_recipe)),
    tar_target(run_softmax, test_model(act1 = "softmax", churn_data, churn_recipe)),
    tar_target(
      best_run,
      bind_rows(run_relu, run_sigmoid, run_softmax) %>%
        top_n(1, accuracy) %>%
        head(1)
    ),
    tar_target(
      best_model,
      retrain_run(best_run, churn_recipe),
      format = "keras"
    )
  )
})
```

What happened when you ran the code chunk above?

A. No targets ran. the `tar_script()` function wrote the code inside the braces to a file called `_targets.R` in your working directory. In real projects, subsequent modifications to `_targets.R` are best done by hand and not through `tar_script()`.
B. Same as A except some targets ran.
C. Same as B except all targets ran.
D. Nothing happened.

```{r}
answer_setup("E")
```

# First target

Run whole the pipeline with `tar_make()`.

```{r}
tar_make()
```

Which target ran first? Why?

A. `churn_data`, because the rest of the targets depend on it.
B. `churn_file`, because the rest of the targets depend on it.
C. `churn_data`, because it appears first in `tar_pipeline()`.
D. `churn_file`, because it appears first in `tar_pipeline()`.

```{r}
answer_first("E") # Supply your own answer here.
```

# Last target

Which target ran last? Why?

A. `best_model`, because it depends on the results of the other targets.
B. `best_model`, because it is listed last in the pipeline.
C. `best_run`, because it depends on the results of the other targets.

```{r}
answer_last("E") # Supply your own answer here.
```

# Inspection

Load the `best_model` target from the `_targets/` data store using the `tar_load()` function. Print the object.

```{r}
tar_load(best_model)
print(best_model)
```

What did you see?

A. A function.
B. A trained Keras model.
C. A one-row data frame.
D. A recipe object.

```{r}
answer_inspect("E") # Supply your own answer here.
```

# Rerun `tar_make()`

Run `tar_make()` again.

```{r}
tar_make()
```

What happened? Why?

A. No target reran because the previous results are already in storage (`_targets/`).
B. `tar_make()` reran the best model.
C. All the targets reran.
D. No target reran because all the targets are already up to date with their dependencies (the underlying code and data, including upstream targets).

```{r}
answer_rerun("E") # Supply your own answer here.
```

# Restart the session

Restart your R session.

```{r}
rstudioapi::restartSession()
source("3-changes/utils.R")
source("3-changes/answers.R")
```

Then, run `tar_make()` again.

```{r}
library(targets)
tar_make()
```

Which targets reran? Why?

A. None. The targets are in storage (in `_targets/objects/`) and are still up to date with their dependencies.
B. I get a confusing error message.
C. All targets reran because I restarted the R session.
D. All the models rerun.

```{r}
answer_restart("E") # Supply your own answer here.
```

# Change the data.

Remove the last row of the dataset.

```{r, message = FALSE}
library(tidyverse)
"data/churn.csv" %>%
  read_csv(col_types = cols()) %>%
  head(n = nrow(.) - 1) %>%
  write_csv("data/churn.csv")
```

Run the pipeline again.

```{r}
tar_make()
```

Which targets reran? Why?

A. All of them. `targets` notices it has been a while since you ran the pipeline.
B. All of them. The data file changed, and `targets` automatically knows `data/churn.csv` is a data file.
C. All of them. The data file changed, and the pipeline automatically tracks `data/churn.csv`. The data file is tracked because `churn_file` is a `tar_target()` with `format = "file"` and the target's return value is `"data/churn.csv"`.
D. None of them, because `data/churn.csv` is neither a target nor a function in the global environment.

```{r}
answer_data("E") # Supply your own answer here.
```

# Change a command.

# Change a function.

# Make a trivial change.
