---
title: "Runtime savings amid rapid change"
output: html_notebook
---

# About

In this chapter, we will put `targets` to the test. We will modify code and data and and watch `tar_make()` run the minimum amount of computation required to bring the results back up to date. This saves time when an ambitious project is still under development and rapidly changing.

# Instructions

Throughout this chapter, you will test your understanding with quiz questions. Supply your choices to the `answer3_*()` functions. Run the code chunk below to set up the quiz questions. Please try not to peak in advance. It is okay to answer incorrectly at first.

```{r}
source("R/quiz.R")
source("3-changes/answers.R")
```

Let's clear out the old `_targets/` data store.

```{r}
library(targets)
tar_destroy() # Start fresh.
```

# Setup

Run the line below to begin with a new `_targets.R` file.

```{r}
tmp <- file.copy("3-changes/initial_targets.R", "_targets.R", overwrite = TRUE)
```

Then, open `_targets.R` in the RStudio IDE.

```{r}
tar_edit()
```

What do you see?

A. A call to `source("3-changes/functions.R")` to load our custom functions.
B. A call to `tar_option_set()` to declare the packages the targets need when they run.
C. The full pipeline from `2-pipelines.Rmd` at the very bottom of the file.
D. All the above.

```{r}
answer3_setup("E") # Supply your own answer here.
```

# First target

Run whole the pipeline with `tar_make()`.

```{r}
tar_make()
```

Which target ran first? Why?

A. `churn_data`, because the rest of the targets depend on it.
B. `churn_file`, because the rest of the targets depend on it.
C. `churn_data`, because it appears first in `tar_pipeline()`.
D. `churn_file`, because it appears first in `tar_pipeline()`.

```{r}
answer3_first("E")
```

# Last target

Which target ran last? Why?

A. `best_model`, because it depends on the results of the other targets.
B. `best_model`, because it is listed last in the pipeline.
C. `best_run`, because it depends on the results of the other targets.
D. `best_run`, because it is listed last in the pipeline.

```{r}
answer3_last("E")
```

# Inspection

Load the `best_model` target from the `_targets/` data store using the `tar_load()` function. Print the object.

```{r}
tar_load(best_model)
print(best_model)
```

What did you see?

A. A function.
B. A trained Keras model.
C. A one-row data frame.
D. A recipe object.

```{r}
answer3_inspect("E")
```

# Rerun `tar_make()`

Run `tar_make()` again.

```{r}
tar_make()
```

What happened? Why?

A. No target reran because the previous results are already in storage (`_targets/`).
B. `tar_make()` reran the best model.
C. All the targets reran.
D. No target reran because all the targets are already up to date with their dependencies (the underlying code and data, including upstream targets).

```{r}
answer3_rerun("E")
```

# Restart the session

Restart your R session.

```{r}
rstudioapi::restartSession()
source("R/quiz.R")
source("3-changes/answers.R")
```

Then, run `tar_make()` again.

```{r}
library(targets)
tar_make()
```

Which targets reran? Why?

A. None. The targets are in storage (`_targets/objects/`) and are still up to date with their dependencies.
B. I get a confusing error message.
C. All targets reran because I restarted the R session.
D. All the models rerun.

```{r}
answer3_restart("E")
```

# Change the data.

Remove the last row of the dataset file `data/churn.csv`.

```{r, message = FALSE}
library(tidyverse)
"data/churn.csv" %>%
  read_csv(col_types = cols()) %>%
  head(n = nrow(.) - 1) %>%
  write_csv("data/churn.csv")
```

Run the pipeline again.

```{r}
tar_make()
```

Which targets reran? Why?

A. All of them. `targets` notices it has been a while since you ran the pipeline.
B. All of them. The data file changed, and `targets` automatically knows `data/churn.csv` is a data file.
C. All of them. The data file changed, and the pipeline is configured to automatically track `data/churn.csv`. The pipeline tracks the data file because the `churn_file` target returns the value `"data/churn.csv"` and the call to `tar_target()` has `format = "file"`.
D. None of them, because `data/churn.csv` is neither a target nor a function in the global environment.

```{r}
answer3_data("E")
```

# Change a command.

Open `_targets.R` for editing in the RStudio IDE. In the command of target `best_run`, change the function to `rbind()` to the preferred `bind_rows()` from `dplyr`. The target definition should look like this:

```{r, eval = FALSE}
tar_target(
  best_run,
  bind_rows(run_relu, run_sigmoid, run_softmax) %>%
    top_n(1, accuracy) %>%
    head(1)
)
```

Then, rerun the pipeline.

```{r}
tar_make()
```

Which targets ran? Why?

A. None. `bind_rows()` and `rbind()` return the same value.
B. None. `targets` can predict that `bind_rows()` and `rbind()` will return the same value.
C. `best_run` and `best_model`. The command of `best_run` changed, and `best_model` is directly downstream.
D. `best_run` only. The command of `best_run` changed, but `best_run` returned the same value, so `best_model` is still up to date.

```{r}
answer3_command("E")
```

# Change a function.

Open `3-changes/functions.R` for editing in the RStudio IDE. In the body of `define_model()`, change the `rate` argument to 0.2 in the first call to `layer_dropout()`.

```{r, eval = FALSE}
layer_dropout(rate = 0.2) # previously 0.1
```

Then, rerun the pipeline.

```{r}
tar_make()
```

Which targets ran? Why?

A. None. No target directly calls `define_model()`.
B. None. The model definition did not change much.
C. `run_relu`, `run_sigmoid`, `run_softmax`, `best_run`, and possibly `best_model`.  `best_model` might not run because it only depends on `best_model`.
D. `run_relu`, `run_sigmoid`, `run_softmax`, `best_run`, and `best_model`.

```{r}
answer3_function("E")
```

# Make a trivial change.

Open `3-changes/functions.R` for editing in the RStudio IDE. Add a comment in the body of `define_model()` and change nothing else.

```{r, eval = FALSE}
define_model <- function(churn_recipe, units1, units2, act1, act2, act3) {
  # This is an arbitrary comment.
  input_shape <- ncol(
    juice(churn_recipe, all_predictors(), composition = "matrix")
  )
  # Leave the rest of the function alone.
}
```

Which targets ran? Why?

A. `run_relu`, `run_sigmoid`, `run_softmax`, `best_run`, and `best_model`. The `define_model()` function changed, which affects all these targets.
B. None. `tar_make()` ignores trivial changes like comments and white space: anything that does not show up in `deparse(define_model)`. 
C. None. `tar_make()` ignores all changes to functions.
D. None. No target directly calls `define_model()`.

```{r}
answer3_trivial("E")
```
