---
title: "Make changes to the workflow"
output: html_notebook
---

# About

When we modify the code and data of an existing workflow, `targets` automatically detects the changes, and `tar_make()` only reruns the affected targets. This notebook showcases this behavior and shows how it can save you time.

# Instructions

Throughout this chapter, you will test your understanding with quiz questions. Supply your choices to the `answer_*()` functions when you come to them. Run the code chunk below to set up the quizzes, but try not to peak in advance.

```{r}
source("3-changes/utils.R")
source("3-changes/answers.R")
```

Let's clear out the old `_targets/` data store if it exists.

```{r}
library(targets)
tar_destroy() # Start fresh.
```

# Setup

Let's begin with a fresh pipeline.

```{r}
tar_script({
  source("3-changes/functions.R")
  tar_option_set(packages = c("keras", "recipes", "rsample", "tidyverse", "yardstick"))
  tar_pipeline(
    tar_target(churn_file, "data/churn.csv", format = "file"), 
    tar_target(churn_data, split_data(churn_file)),
    tar_target(churn_recipe,  prepare_recipe(churn_data)),
    tar_target(run_relu, test_model(act1 = "relu", churn_data, churn_recipe)),
    tar_target(run_sigmoid, test_model(act1 = "sigmoid", churn_data, churn_recipe)),
    tar_target(run_softmax, test_model(act1 = "softmax", churn_data, churn_recipe)),
    tar_target(
      best_run,
      bind_rows(run_relu, run_sigmoid, run_softmax) %>%
        top_n(1, accuracy) %>%
        head(1)
    ),
    tar_target(
      best_model,
      retrain_run(best_run, churn_recipe),
      format = "keras"
    )
  )
})
```

What happened when you ran the code chunk above?

A. No targets ran. the `tar_script()` function wrote the code inside the braces to a file called `_targets.R` in your working directory. In real projects, subsequent modifications to `_targets.R` are best done by hand and not through `tar_script()`.
B. Same as A except some targets ran.
C. Same as B except all targets ran.
D. Nothing happened.

```{r}
answer_setup("E")
```

# First target

Run whole the pipeline with `tar_make()`.

```{r}
tar_make()
```

Which target ran first? Why?

A. `churn_data`, because the rest of the targets depend on it.
B. `churn_file`, because the rest of the targets depend on it.
C. `churn_data`, because it appears first in `tar_pipeline()`.
D. `churn_file`, because it appears first in `tar_pipeline()`.

```{r}
answer_first_target("E") # Supply your own answer here.
```
