---
title: "Custom functions for the customer churn workflow"
output: html_document
---

# About

`targets` can watch input files, output files, and literate programming documents for changes. This chapter explores how to configure a target to automatically run when a file changes.

# Setup

Run `tar_destroy()` to remove the targets from the previous chapter.

```{r}
library(targets)
tar_destroy()
```

Load this chapter's quiz questions. Try not to peek in advance.

```{r}
source("R/quiz.R")
source("4-files/answers.R")
```

Run the following command to write the required `_targets.R` script to the your working directory.

```{r, echo = FALSE}
file.copy("4-files/initial_targets.R", "_targets.R", overwrite = TRUE)
```

Open `_targets.R` for editing

```{r}
library(usethis)
edit_file("_targets.R", open = TRUE)
```

# Review: input data files

As we saw in `3-changes.Rmd`, `targets` can watch files like `data/churn.csv` for changes. Let's review how this works. First, run the full pipeline from start to finish.

```{r}
tar_make()
```

Verify that all targets are now up to date.

```{r}
tar_make()
```

Now, open the customer churn data file for editing. Manually remove the last line of data in the file.

```{r}
edit_file("data/churn.csv")
```

When we call `tar_make()` again, all targets should rerun because they all depend on the upstream file target `churn_file`.

```{r}
tar_make()
```

How do we configure `churn_file` and downstream targets to rerun when `data/churn.csv` changes?

A. The target's return value needs to be a character vector of file and directory paths. These paths get resolved at runtime, so we do not need to know them before we call `tar_make()`. 
B. In `tar_target()`, set the `format` argument equal to `"file"`. That way, `tar_make()` knows the return value of `churn_file` is a bunch of file paths that need to be watched.
C. Targets directly downstream need to mention the symbol `churn_file` (as opposed to the literal path `"data/churn.csv"`) so `tar_make()` can discover the correct dependency relationships among targets. Always check with `tar_visnetwork()` to verify that your targets are connected properly in the dependency graph.
D. All the above.

```{r}
answer_review("E")
```

# Output files

In `targets`, we configure output files the exact same way. The only difference between input and output files is that output files are created when the target runs.

As an example, open `_targets.R` and create a new file targets `churn_cor`, which saves a CSV file and a plot of correlations (the correlation of each covariate with customer churn in the preprocessed testing data). Functions `compute_cor()` and `plot_cor()` in `4-files/functions.R` do most of the work.

```{r}
edit_file("_targets.R", open = TRUE)
```

Enter the new target below into `tar_pipeline()` in `_targets.R`.

```{r, eval = FALSE}
tar_target(
  churn_cor, {
    cor <- compute_cor(churn_recipe)
    plot <- plot_cor(cor)
    write_csv(cor, "cor.csv")
    ggsave(plot = plot, filename = "cor.png", width = 8, height = 8)
    # The return value must be a vector of paths to the files we write:
    paste0("cor.", c("csv", "png"))
  },
  format = "file" # Tells targets to track the return value (path) as a file.
)
```

Run the pipeline. Since all previous targets are up to date, only `churn_cor` should run.

```{r}
tar_make()
```

What is the return value of the new `churn_cor` target?

```{r}
tar_read(churn_cor)
```

A. `c("cor.csv", "cor.png")`, a vector of paths to the files produced by the target.
B. A `ggplot` object with the correlation plot.
C. A data frame of correlations.
D. A function called `churn_cor()`.

```{r}
answer_return("E")
```

Take a look at the new output file `cor.png`. You should see a plot of each variable's correlation with customer churn. Also glance at `cor.csv`, the output dataset with the correlations.

```{r}
read_csv("cor.csv", col_types = cols())
```

Now, delete one of the files and rerun the pipeline.

```{r}
tmp <- file.remove("cor.png")
tar_make()
```

What happened? Why?

A. All targets reran because we changed a file.
B. No target reran because `targets` does not track the deleted file.
C. Because `churn_cor` is a correctly configured file target, `tar_make()` noticed when `cor.png` changed and automatically reran in order to repair the file.
D. `churn_cor` because `targets` always treats character strings as file names.

```{r}
answer_delete("E")
```

Whenever a single target like `churn_cor` tracks multiple files or directories, `tar_make()` treats all those files as a single unit. The whole target invalidates when one of the files changes, and downstream targets must accept all the files together. When we come to the chapter on branching, we will use the special `tar_files()` function from the `tarchetypes` package to branch over the available files.

# Literate programming
 
Literare programming is the practice of writing code and explanatory prose in the same source file, such as this R Markdown document. We have already been using literate programming / R Markdown on top of `targets`. In this section, we will explore literate programming as a piece of a `targets`-powered workflow.

The R Markdown report in `4-files/results.Rmd` uses `tar_read()` and `tar_load()` to load targets we previously built, and it has prose to explain the meaning of each target so others can better understand our research.

Copy `4-files/results.Rmd` to the working directory and open the file for editing. Locate the calls to `tar_read()` and `tar_load()` in the active code chunks.

```{r}
tmp <- file.copy("4-files/results.Rmd", "results.Rmd", overwrite = TRUE)
edit_file("results.Rmd", open = TRUE)
```

## R Markdown on its own

Because we ran the pipeline before, our targets live in the `_targets/` data store. Switch back to `results.Rmd` in the RStudio IDE  and click the `knit` button to generate the output file `results.html`. Then, view `results.html` in the IDE or a web browser. Alternatively, you can render and view the report with the following code.

```{r}
library(rmarkdown)
render("results.Rmd")
browseURL("results.html")
```

## R Markdown inside a target

For the sake of convenience and reproducibility, we can render this report inside a target in the pipeline. That way, `targets` will automatically regenerate `results.html` whenever its dependencies change. The `tar_render()` function from the `tarchetpyes` package is the correct way to include an R Markdown report with dependencies. It automatically creates a target that reproducibly tracks the R Markdown source file, the rendered output file, and the target dependencies mentioned with `tar_load()` and `tar_read()`.

Open `_targets.R` for editing.

```{r}
edit_file("_targets.R", open = TRUE)
```

Write `library(tarchetypes)` at the very top, and write `tar_render(report_step, "results.Rmd")` as a target in the pipeline. Sketch:

```{r, eval = FALSE}
library(tarchetypes)
# Existing setup code goes here.
tar_pipeline(
  # Existing calls to tar_target() stay here.
  tar_render(report_step, "results.Rmd")
)
```

To check your work, take a look at the dependency graph.

```{r}
tar_visnetwork()
```

What are the dependencies of the `report_step` target?

Which target(s) does `results.Rmd` depend on? Why?

A. None. `results.Rmd` is not a target or a pipeline.
B. `run_relu` becuase the report calls `tar_read(run_relu)` in an active code chunk.
C. `run_sigmoid` because the report calls `tar_load(run_sigmoid)` in an active code chunk.
D. `run_relu` and `run_sigmoid` because the report calls `tar_read(run_relu)` and `tar_load(run_sigmoid)` in active code chunks.

```{r}
answer_deps1("E")
```

## Add a dependency

At the bottom of the `report.Rmd`, add an active code chunk to print out the best model (`tar_read(best_model)`). Then, look at the graph again.

```{r}
tar_visnetwork().
```

What changed? Why?

A. `report_step` is disconnected from the other nodes in the graph because we edited the report.
B. The graph did not change because we did not run the report yet.
C. `report_step` now depends on `best_model` in addition to `run_relu` and `run_sigmoid`. All three are mentioned in active code chunks with `tar_load()` and `tar_read()`.
D. `report_step` is only connected to `best_model` now because you just added it as a dependency.

```{r}
answer_deps2("E")
```

## Run the report

Run the whole pipeline. The newly added `report_step` target should run. 

```{r}
tar_make()
```

Verify that all targets are up to date now.

```{r}
tar_make() # See also tar_outdated()
```

View `results.html`. You should see a print-out of the best model at the bottom.

```{r}
browseURL("results.html")
```

## Remove the output file

Remove the output HTML file.

```{r}
unlink("results.html")
```

What happened? Why?

A. All targets reran because the file system change.
B. The `report_step` target reran because `tar_render()` reproducibly tracks the output files of `rmarkdown::render()` and helps `tar_make()` respond to changes in `results.html`.
C. The `report_step` target reran because `results.Rmd` changed.
D. No targets reran because output files from R Markdown reports are not reproducibly tracked.

```{r}
answer_html("E")
```

## Change the R Markdown source

Add some prose anywhere in the body of `results.Rmd`.

```{r}
edit_file("results.Rmd", open = TRUE)
# Edit the file to add comments to explain the results.
```

Now, rerun the pipeline.

```{r}
tar_make()
```

What happened? Why?

A. Only `report_step` reran becasue the R Markdown source file changed and all the other targets stayed up to date.
B. Only `report_step` reran because R Markdown reports always rerun.
C. All targets reran because `results.Rmd` is a dependency of the whole pipeline.
D. No targets reran because the pipeline does not track changes to the R Markdown source.

```{r}
answer_rmd("E")
```

## Change a dependency target

Open the file `data/churn.csv` and remove the last row in the dataset.

```{r}
edit_file("data/churn.csv", open = TRUE)
```

Now, rerun the pipeline.

Did `report_step` rerun? Why?

A. No, because `data/churn.csv` is not a dependency of `report_step`.
B. No, because the `report.Rmd` does not read `data/churn.csv`.
C. Yes. The R Markdown report is downstream of a target that depends on `data/churn.csv`, and the change in the data file caused a chain reaction that invalidated `report_step`.
D. Yes. If a single target imports a data file, all targets in the pipeline rerun.

```{r}
answer_rmd_data("E")
```
