---
title: "Interactive debugging"
output: html_document
---

# Setup

Start with a fresh data store.

```{r}
library(targets)
tar_destroy()
```

Copy the starting `_targets.R` file into the working directory.

```{r}
tmp <- file.copy("6-debugging/initial_targets.R", "_targets.R", overwrite = TRUE)
```

# Problem

This pipeline has a bug, and it only happens in one of the models. Your job is to find and fix it.

```{r}
tar_make()
```

```{r}
tar_visnetwork()
```

To begin to search for clues, review the error message and warnings stored in the metadata. Make a note of the branch of `run` that threw the error.

```{r}
tar_meta(starts_with("run"), fields = c("error", "warnings"))
```

# Debugging with saved workspaces

We need more information, so we invoke `tar_make()` with interactive debugging. First, open `_targets.R` for editing.

```{r}
tar_edit()
```

In `tar_option_set()`, set `error` to `"save"`. Next time a target errors out, `targets` will save a workspace image file in `_targets/workspaces/`.

```{r, eval = FALSE}
# Do not run here.
tar_option_set(
  packages = c(
    "corrr",
    "keras",
    "recipes",
    "rsample",
    "tidyverse",
    "yardstick"
  ),
  error = "save"
)
```

Now, run `tar_make()` and let the error happen again.

```{r}
tar_make()
```

Find the name of the failed target.

```{r}
library(tidyverse)
failed <- tar_meta(fields = error) %>%
  na.omit() %>%
  pull(name) %>%
  head(n = 1)
print(failed)
```

Confirm that a saved workspace exists for this target.

```{r}
list.files("_targets/workspaces")
```

Load the workspace of this target to restore the packages, environment, and random number generator seed that were loaded when the target errored out.

```{r}
tar_workspace(run_________) # Supply the failed target name.
```

You environment should now have the correct values of `activations`, `units`, `churn_data`, and `churn_recipe` to supply to `test_model(act1 = activations, units1 = units, churn_data, churn_recipe)` (the target's command).

```{r}
print(activations) # Should be a scalar.
print(units) # Should be a scalar.
```

You should now be able to run the target's command and reproduce the error without `tar_make()`

```{r}
test_model(act1 = activations, units1 = units, churn_data, churn_recipe)
```

# Your turn

Now go find that error and fix it! You have completed the exercise when `tar_make()` runs without error. Once you are done, remove the workspace files using `tar_undebug()`. This is good practice because workspace files can get quite large.

# Tip: interactive debugging

Base utilities `debug()`, `debugonce()`, `undebug()`, and `browse()` are extremely helpful for debugging functions. More information on interactive debugging can be found at <https://rstats.wtf/debugging-r-code.html>.

```{r}
debugonce(test_model)
test_model(act1 = activations, units1 = units, churn_data, churn_recipe)
```

Once you are inside the debugger, you can access objects in the runtime environment and gradually step through the code. Press `n` to advance to the next line, and press `c` to continue on to the next breakpoint (place where the debuggger pauses). Press `Q` to exit the debugger.

# Interactive debugging in `targets`

As an alternative technique, you can debug interactively while `tar_make()` is actually running. Set these options in `_targets.R`.

```{r}
tar_option_set(debug = "run_________", cue = tar_cue(mode = "never"))
```

Then, restart R and run `tar_make(callr_function = NULL)`. `targets` will drop you into an interactive debugger at the errored target.

```{r}
tar_make(callr_function = NULL)
```

Some situations may require you to debug this way instead of `error = "save"`. For example, if some of your target's dependencies cannot be serialized with `qs::qsave()` (e.g. Keras model objects) then the workspace cannot be saved properly.
